---
title: "Technical Background"
author: "Madeline Gorchels"
date: "5/28/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(tidyverse)
library(RColorBrewer)
```



```{r}
carbon = read_csv("HW4Data.csv")
```
Part 1 
Write down a plausible functional form for the marginal cost of abatement for sector A. Use regression
analysis to estimate the parameters of that function. Repeating this for sectors B, C, and D will give
you a model of the marginal cost of abatement function for each sector. How well do your models fit
the data for each sector? You may need to experiment with different functional forms. Produce a plot
of the estimated marginal abatement cost functions in all four sectors (this plot should go in your
memo).

Just use linear because it's easier to integrate 
```{r}
ggplot(carbon, aes(x=Abatement, y = MC_A))+
  geom_point()+
  theme_classic()
```
```{r}
sectorA = lm(data = carbon, MC_A~Abatement)
summary(sectorA)

sectorB = lm(data = carbon, MC_B~Abatement)
summary(sectorB)

sectorC = lm(data = carbon, MC_C~Abatement)
summary(sectorC)

sectorD = lm(data = carbon, MC_D~Abatement)
summary(sectorD)
```


```{r}
#Plotting the estimated marginal abatement cost functions in all four sectors

#mac_fun <- ggplot(carbon, aes(x = "Tons of CO2", y = "Cost")) +
       #geom_point() +
  #stat_smooth(method = "lm", col = "red")
  #scale_y_continuous(expand = c(0,0)) +
  #scale_x_continuous(expand = c(0,0)) +
  #geom_ribbon(aes(ymin = Probability - SE, ymax = Probability + SE, fill = Sex), alpha = 0.3) +
  #theme_classic()

#ggplot(iris, aes(x = Petal.Width, y = Sepal.Length)) + 
  #geom_point() +
  #stat_smooth(method = "lm", col = "red")

mac_funs <- ggplot(carbon) +
  geom_smooth(aes(Abatement,MC_A, colour="A"), method=lm, se=FALSE) +
  geom_smooth(aes(Abatement,MC_B,colour="B"), method=lm, se=FALSE) +
  geom_smooth(aes(Abatement,MC_C, colour="C"), method=lm, se=FALSE) +
  geom_smooth(aes(Abatement,MC_D, colour="D"), method=lm, se=FALSE) +
  labs(x = "CO2 (Tons)", y = "Cost ($)") +
  theme_classic()+
  scale_fill_discrete(name="Sector")

mac_funs


```


Part 2 

```{r}
#Calculating the y intercept for the demand function can be accomplished because they won't pay more than this amount
sectorAmp = sectorA$coefficients[2]*180 + sectorA$coefficients[1]

sectorBmp = sectorB$coefficients[2]*200 + sectorB$coefficients[1]

sectorCmp = sectorC$coefficients[2]*220 + sectorC$coefficients[1]

sectorDmp = sectorD$coefficients[2]*300 + sectorD$coefficients[1]



#SectorA Demand Curve
SectorADemand = function(x) {
  Demand = (sectorAmp/A)*x + A
}
#SectorB Demand Curve
SectorBDemand = function(x) {
  Demand = (sectorBmp/B)*x + B
}
#SectorC Demand Curve
SectorCDemand = function(x) {
  Demand = (sectorCmp/C)*x + C
}
#SectorD Demand Curve
SectorDDemand = function(x) {
  Demand = (sectorDmp/D)*x + D
}

```

Part 3

```{r}
A = 180
B = 200
C = 220
D = 300
A+B+C
#needs to cut by 300
```
3. Now focus on country X (which contains sectors A, B, and C). Assume there are no “co-benefits” from
carbon abatement (i.e. that there are no local pollutants that are affected by carbon abatement).
Suppose to meet the Paris Accord commitments, country X needs to cut all carbon emissions in half.
For each of the policy options listed below, derive: (1) the total cost of meeting the target in country X,
(2) the cost (or benefit) to each sector, and (3) the tax revenue generated.
a. Cap on carbon. Each sector (A, B, and C) must cut its carbon emissions by 100 tons (thus
reducing total emissions from 600 down to 300).

```{r}

```


b. Tax on carbon. To emit a ton of carbon in country X, you must pay a tax of $t. You will need to
find the tax that accomplishes the desired reduction.
c. Cap and trade. Each sector (A, B, C) is allocated carbon permits equal to their current emissions
minus 100 (same as in (a) above), thus achieving the total reduction of 300. Then, these three
sectors are allowed to trade with each other. You will need to derive the outcome of that
trading.
