---
title: "Technical Background"
author: "Madeline Gorchels"
date: "5/28/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
library(tidyverse)
```



```{r}
carbon = read_csv("HW4Data.csv")
```

Write down a plausible functional form for the marginal cost of abatement for sector A. Use regression
analysis to estimate the parameters of that function. Repeating this for sectors B, C, and D will give
you a model of the marginal cost of abatement function for each sector. How well do your models fit
the data for each sector? You may need to experiment with different functional forms. Produce a plot
of the estimated marginal abatement cost functions in all four sectors (this plot should go in your
memo).

Just use linear because it's easier to integrate 
```{r}
ggplot(carbon, aes(x=Abatement, y = MC_A))+
  geom_point()+
  theme_classic()
```
```{r}
sectorA = lm(data = carbon, MC_A~Abatement)
summary(sectorA)

sectorB = lm(data = carbon, MC_B~Abatement)
summary(sectorB)

sectorC = lm(data = carbon, MC_C~Abatement)
summary(sectorC)

sectorD = lm(data = carbon, MC_D~Abatement)
summary(sectorD)
```

Part 3

```{r}
A = 180
B = 200
C = 220
D = 300
A+B+C
#needs to cut by 300
```

